Supporting information: Copulas and their potential for ecology

### 2019-12-17 Paper.Rmd
caption edited

<!--adding plots showing influences of non-normal copula on spatial Taylors law-->
\begin{figure}[!h]
\textbf{ \hspace{2cm} (A) \hspace{2.92 cm} (B) \hspace{2.92 cm} (C) \hspace{2.92 cm} (D)} \\
\vspace{-0.8 cm} 
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png}\\
\end{center}
\textbf{ \hspace{1 cm} (E) \hspace{1.4 cm} (F) \hspace{1.2 cm} (G) \hspace{1.2 cm} (H) \hspace{1.4 cm} (I) \hspace{1.4 cm} (J) \hspace{1.2 cm} (K)}\\
\vspace{-0.8 cm}
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf}
\caption[Spatial Taylor's law results]{Spatial Taylor's law results. Log(spatial variance) vs. 
log(spatial mean) relationships for $1000$ simulations over $50$ time steps for $25$ locations 
using Clayton (A), normal (B), Frank (C), and survival Clayton (D) copula structures between
locations. Results from all $1000$ 
simulations were plotted on the same axes for each panel, but two example simulations are 
shown in solid and void black dots to help assess to what extent variation on the plots was between 
simulations or within simulations. For each simulation, we tested the linearity 
(E) and homoskedasticity (F) of the log(variance) vs. log(mean) plot for that simulation, 
and quantified the root mean squared error of points from the linear regression line (G).
We also calculated the linear regression intercept (H) and slope (I), the quadratic
term of a quadratic regression through the points on the log(variance) vs. log(mean) plot
(J), and the curvature of that quadratic regression (K). Distributions of values 
across all 1000 simulations are displayed. Spearman-preserving surrogates were used, 
though results using Kendall-preserving surrogates were similar. See section \ref{Consequences}
and Appendices \ref{SM-Consequence_TL_simulation} and 
\ref{SM-sect:copsurrognd} for details.\label{fig_spTL}}
\end{center}
\end{figure}

>>>>

<!--adding plots showing influences of non-normal copula on spatial Taylors law-->
\begin{figure}[!h]
\textbf{ \hspace{2cm} (A) \hspace{2.92 cm} (B) \hspace{2.92 cm} (C) \hspace{2.92 cm} (D)} \\
\vspace{-0.8 cm} 
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png}\\
\end{center}
\textbf{ \hspace{1 cm} (E) \hspace{1.4 cm} (F) \hspace{1.2 cm} (G) \hspace{1.2 cm} (H) \hspace{1.4 cm} (I) \hspace{1.4 cm} (J) \hspace{1.2 cm} (K)}\\
\vspace{-0.8 cm}
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf}
\caption[Spatial Taylor's law results]{Spatial Taylor's law results. Log(spatial variance) vs. 
log(spatial mean) relationships for $1000$ simulations over $50$ time steps for $25$ locations 
using Clayton (A), normal (B), Frank (C), and survival Clayton (D) copula structures between
locations. Results from all $1000$ 
simulations were plotted on the same axes for each panel, but two example simulations are 
shown in solid and void black circles to help assess to what extent variation on the plots was between 
simulations or within simulations. For each simulation, we tested the linearity 
(E) and homoskedasticity (F) of the log(variance) vs. log(mean) plot for that simulation, 
and quantified the root mean squared error of points from the linear regression line (G).
We also calculated the linear regression intercept (H) and slope (I), the quadratic
term of a quadratic regression through the points on the log(variance) vs. log(mean) plot
(J), and the curvature of that quadratic regression (K). Distributions of values 
across all 1000 simulations are displayed. Spearman-preserving surrogates were used, 
though results using Kendall-preserving surrogates were similar. See section \ref{Consequences}
and Appendices \ref{SM-Consequence_TL_simulation} and 
\ref{SM-sect:copsurrognd} for details.\label{fig_spTL}}
\end{center}
\end{figure}

### 2019-12-17 SupportingInformation.Rmd
caption edited

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.png",width=16,height=4,units="in",res=400)
op<-par(mfrow=c(1,4),mar=c(8,8,2,1),mgp=c(4,1,0))
##plot TL for clayton
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[1]][,1,1],kend.points.res[[1]][,2,1],type='p',pch=19,cex=.75,col='black')
points(kend.points.res[[1]][,1,2],kend.points.res[[1]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black",cex=2)

##plot TL for normal copula
plot(kend.points.res[[2]][,1,],kend.points.res[[2]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[2]][,1,1],kend.points.res[[2]][,2,1],type='p',pch=19,cex=.75,col='black')
points(kend.points.res[[2]][,1,2],kend.points.res[[2]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Normal"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for frank
plot(kend.points.res[[3]][,1,],kend.points.res[[3]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[3]][,1,1],kend.points.res[[3]][,2,1],type='p',pch=19,cex=.75,col='black')
points(kend.points.res[[3]][,1,2],kend.points.res[[3]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for survival clayton
plot(kend.points.res[[4]][,1,],kend.points.res[[4]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[4]][,1,1],kend.points.res[[4]][,2,1],type='p',pch=19,cex=.75,col='black')
points(kend.points.res[[4]][,1,2],kend.points.res[[4]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Survival Clayton"),side=3, line=-2, adj=0.1, col="black",cex=2)

@@

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png",height=4,width=16,units="in",res=400)
op<-par(mfrow=c(1,4),mar=c(8,8,2,1),mgp=c(4,1,0))
##plot TL for clayton
plot(spea.points.res[[1]][,1,],spea.points.res[[1]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[1]][,1,1],spea.points.res[[1]][,2,1],type='p',pch=19,cex=.75,col='black')
points(spea.points.res[[1]][,1,2],spea.points.res[[1]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Clayton"),side = 3, line=-2.5, adj=0.1, col="black",cex=2)

##plot TL for normal copula
plot(spea.points.res[[2]][,1,],spea.points.res[[2]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[2]][,1,1],spea.points.res[[2]][,2,1],type='p',pch=19,cex=.75,col='black')
points(spea.points.res[[2]][,1,2],spea.points.res[[2]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Normal"),side = 3, line=-2.5, adj=0.1, col="black",cex=2)

#plot TL for frank
plot(spea.points.res[[3]][,1,],spea.points.res[[3]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[3]][,1,1],spea.points.res[[3]][,2,1],type='p',pch=19,cex=.75,col='black')
points(spea.points.res[[3]][,1,2],spea.points.res[[3]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for survival clayton
plot(spea.points.res[[4]][,1,],spea.points.res[[4]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[4]][,1,1],spea.points.res[[4]][,2,1],type='p',pch=19,cex=.75,col='black')
points(spea.points.res[[4]][,1,2],spea.points.res[[4]][,2,2],type='p',pch=1,cex=.75,col='black')
mtext(paste("Survival Clayton"),side=3, line=-2.5, adj=0.1, col="black",cex=2)

>>>>

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.png",width=16,height=4,units="in",res=400)
op<-par(mfrow=c(1,4),mar=c(8,8,2,1),mgp=c(4,1,0))
##plot TL for clayton
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[1]][,1,1],kend.points.res[[1]][,2,1],type='p',pch=19,cex=2,col='black')
points(kend.points.res[[1]][,1,2],kend.points.res[[1]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black",cex=2)

##plot TL for normal copula
plot(kend.points.res[[2]][,1,],kend.points.res[[2]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[2]][,1,1],kend.points.res[[2]][,2,1],type='p',pch=19,cex=2,col='black')
points(kend.points.res[[2]][,1,2],kend.points.res[[2]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Normal"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for frank
plot(kend.points.res[[3]][,1,],kend.points.res[[3]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[3]][,1,1],kend.points.res[[3]][,2,1],type='p',pch=19,cex=2,col='black')
points(kend.points.res[[3]][,1,2],kend.points.res[[3]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for survival clayton
plot(kend.points.res[[4]][,1,],kend.points.res[[4]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(kend.points.res[[4]][,1,1],kend.points.res[[4]][,2,1],type='p',pch=19,cex=2,col='black')
points(kend.points.res[[4]][,1,2],kend.points.res[[4]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Survival Clayton"),side=3, line=-2, adj=0.1, col="black",cex=2)

@@

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png",height=4,width=16,units="in",res=400)
op<-par(mfrow=c(1,4),mar=c(8,8,2,1),mgp=c(4,1,0))
##plot TL for clayton
plot(spea.points.res[[1]][,1,],spea.points.res[[1]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[1]][,1,1],spea.points.res[[1]][,2,1],type='p',pch=19,cex=2,col='black')
points(spea.points.res[[1]][,1,2],spea.points.res[[1]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Clayton"),side = 3, line=-2.5, adj=0.1, col="black",cex=2)

##plot TL for normal copula
plot(spea.points.res[[2]][,1,],spea.points.res[[2]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[2]][,1,1],spea.points.res[[2]][,2,1],type='p',pch=19,cex=2,col='black')
points(spea.points.res[[2]][,1,2],spea.points.res[[2]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Normal"),side = 3, line=-2.5, adj=0.1, col="black",cex=2)

#plot TL for frank
plot(spea.points.res[[3]][,1,],spea.points.res[[3]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[3]][,1,1],spea.points.res[[3]][,2,1],type='p',pch=19,cex=2,col='black')
points(spea.points.res[[3]][,1,2],spea.points.res[[3]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for survival clayton
plot(spea.points.res[[4]][,1,],spea.points.res[[4]][,2,],type='p',pch=19,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3,col="grey")  
points(spea.points.res[[4]][,1,1],spea.points.res[[4]][,2,1],type='p',pch=19,cex=2,col='black')
points(spea.points.res[[4]][,1,2],spea.points.res[[4]][,2,2],type='p',pch=1,cex=2,col='black')
mtext(paste("Survival Clayton"),side=3, line=-2.5, adj=0.1, col="black",cex=2)
